---
title: "Web Api"
author: "Balaji Ramkumar and Amish Satish"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

###This assignment is a task to create a package that works with establishing a connection with a web api. This packages basically uses two web api:-

* Google distance  matrix api.
* Google geo code api.

###The function ***func1()*** accepts two arguements:-

* origin
* destination

The input and output should be a character which is the name of two cities. The function will throw an error if the input is not a character.

```{r, eval=FALSE, include=TRUE}
url1<-"https://maps.googleapis.com/maps/api/distancematrix/json?units=metric&origins="
  url1<-paste(url1,origin,"&destinations=",destination,"&key=AIzaSyB47VpiErStMPVbFHQxueDYN0-hnDu4l-U",sep = "",collapse = NULL)
  sample1<-fromJSON(url1,flatten = TRUE)
  url2<-paste("https://maps.googleapis.com/maps/api/geocode/json?address=",origin,",+CA&key=AIzaSyD7TlapnNso6QUYkh0c17n97qDgEvJBERk",sep = "",collapse = NULL)
  sample2<-fromJSON(url2,flatten = TRUE)
  url3<-paste("https://maps.googleapis.com/maps/api/geocode/json?address=",destination,",+CA&key=AIzaSyD7TlapnNso6QUYkh0c17n97qDgEvJBERk",sep = "",collapse = NULL)
  sample3<-fromJSON(url3,flatten = TRUE)
```


**url1**  is used to get the Google Distance Matrtix. **url2** and **url3** are used to get the geo code of origin and destination.


The main task of this assignment is to learn to create a shiny application. The output should also be displayed in shiny application.

```{r, eval=FALSE, include=TRUE}

 output$map <- renderLeaflet({
        leaflet() %>%
          addTiles(
            urlTemplate = "//{s}.tiles.mapbox.com/v3/jcheng.map-5ebohr46/{z}/{x}/{y}.png",
            attribution = 'Maps by <a href="http://www.mapbox.com/">Mapbox</a>'
          ) %>%
          
          addAwesomeMarkers(lng= c(lnn1,lnn2), lat= c(ltt1,ltt2))
```        



This is the code which was used to display points on the map.

###Much of information on how to create the shiny app was taken from [here](https://shiny.rstudio.com/tutorial/written-tutorial/lesson5/)



